---
title: "Fashion Product Similarity Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css: ressources/theme-dashboard.css
    logo: ressources/jumper_small.png
    favicon: ressources/jumper.ico
    navbar:
      - { title: "Github", icon: "fa-github", href: "https://github.com/matbmeijer/fashion_product_similarity_dashboard", target: "Github"}
params:
    directory: "C:/Users/03739660/OneDrive - Mango/documents/advanced_analytics/r_scripts/fashion_product_similarity_dashboard/silver/dashboard_datatable.rds"
---


```{r setup, include=FALSE}
library(flexdashboard)
library(DT)
```

Column {.tabset}
-------------------------------------
### Image Similarity Examples

```{r}
tbl <- readRDS(params$directory)
tbl
```

### General Information

#### Data
The images were scraped from the fashion retailer [C&A](https://www.c-and-a.com/es/es/shop). The fashion retailer was chosen because it has an image of each product without any person/model and white background, making the images quite homogeneous. The [robots.txt](https://www.c-and-a.com/robots.txt) file as been checked to ensure no infringements are done during scraping.

#### Methodology

Image similarity is a subjective term, as it is difficult to determine similarity on which terms: quality, visual similarity, form, color? At the same time, the importance of each aspect might be different for every person.

The following methodology approaches this problem in simple terms: similarity is defined by the visual characteristics that help to determine the categorization of a fashion product.

An important point to note is that there is no **ground truth** for product similarity.

Taking into account that we define similarity by the characterstics that help to determine the categorization of a product, a neural network for product categorization might be helpful in some way.

This is exactly what is used in this case:
The weights of the pretrained VGG16 model trained on the [Imagenet Dataset](https://www.image-net.org/) are used. As we are not interested in the classification of the product, but the dimensionality that determine the cassification, a global average pooling will be applied to the output of the last convolutional block to define a dimensional space for each fashion item.

For further information visit the [Github repository](https://github.com/matbmeijer/fashion_product_similarity_dashboard)
